---
title: "Reproducibility Report for MA147"
author: "Steven Kambouris"
date: "18/09/2021"
output: html_document
knit: (function(input, ...){
    rmarkdown::render(input, output_dir = here::here("output"), envir = globalenv())
  })
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      include = TRUE)
```

# Reproducing result from

Holman, L. (2016). Bet hedging via multiple mating: A meta-analysis. _Evolution_, _70_(1), 62–71. https://doi.org/10.1111/evo.12822

# Result to be reproduced

> Figure 2 shows the estimated increase in fitness (in percentage points) experienced by a multiple-mating genotype relative to a single-mating genotype ($\Delta_{W}$), assuming that multiple mating has no direct costs or benefits ($\mu_{\textrm{Single}} = \mu_{\textrm{Multiple}}$), and that the effective population size is small ($N_{e} = 10$). The consensus estimate of $\Delta_{Wp=0}$ from meta-analysis was 0.13% (SE = 0.030, 95% CIs: 0.074–0.19)... (Holman, 2016, pp.66-69)

Earlier on p.66, the article states that there were estimates of $\Delta_{Wp=0}$ from 49 studies, implying the sample size is 49.

```{r orig-result}
orig_result_df <- data.frame(ID = "MA147",
                             source = "original",
                             result_type = "mean",
                             es_type = "percentage",
                             point_est = 0.13,
                             se = 0.030,
                             ci_lower = 0.074,
                             ci_upper = 0.19,
                             n = 49)

knitr::kable(x = orig_result_df)
```

# Details of shared data and code files

The following data and code files were shared on Dryad:

Holman, L. (2015). _Data from: Bet hedging via multiple mating: A meta-analysis._ Dryad Digital Repository. https://doi.org/10.5061/dryad.b6d75

* Dataset info.csv
* Holman bet hedging - functions.R
* Holman bet hedging - open this one to run the analysis.R
* README.txt
* Varying N analyses.zip
* Varying p analyses.zip

These files are licensed under a [CC0 1.0 Universal (CC0 1.0) Public Domain Dedication](https://creativecommons.org/publicdomain/zero/1.0/) license.

# Applicability of shared data and code files

## Data
The Dryad repository web page contains Usage Notes, and the respository includes a readme file (`README.txt`). The usage notes and readme file indicate that the data files relevant to the selected result (i.e. when there is a fixed effective population size) are the 147 CSV files contained within the archive `Varying N analyses.zip`.

## Code
The usage notes and readme file indicate that the helpfully-named file `Holman bet hedging - open this one to run the analysis.R` is the code file to use to reproduce the results in the article. The file contains a large number of comments providing instructions on how to run the analysis, including specifically the selected result. (This code file invokes the file `Holman bet hedging - functions.R` which contains custom functions required for running the analysis.)

# Set up
```{r library}

# Load packages required for working with original files.
library(here)

# Load custom package for (i) running the source command for specific line
# numbers within a file and (ii) for calculating the percentage error between
# the original and reproduced values.
library(reprohelper)

# Load packages required for data import/cleaning.
# (None required.)

# Load packages required by the code to run.
# (These packages are loaded in the same order as loaded in the original code
# file.)
library(metafor)
library(reshape2)
library(truncnorm)
library(boot)
library(ggplot2)
library(lme4)

# Set the path to the original code file(s).
orig_source1 <- here::here("original",
"Holman_bet_hedging_-_open_this_one_to_run_the_analysis.R")
orig_source2 <- here::here("original", 
                           "Holman_bet_hedging_-_functions.R")

# The original script assumes a very specific folder structure that has been
# recreated within the folder "original". The code makes reference to a
# variable "main.directory", which is the base folder containing this
# structure. This needs to be set explicitly in order for the code to run as
# intended (the value provided in the original code is the author's own
# computing environment).
main.directory <- "original"

```

# Import and clean data
```{r importdata}

# The original script assumes a very specific folder structure that has been
# recreated here: the "Varying N" CSV files are presumed to be at the following
# location:
# <working directory>/Results of analyses/Varying N analyses/
#
# The code that imports the 147 CSV files from the above folder can be run
# if the variable "main.directory" is set to the folder which contains the
# base folder.
sourceLines(orig_source1, 53, 53)

```

# (Re-)run the analysis to reproduce result
```{r analysis}

# Load all custom functions included in Holman_bet_hedging_-_functions.R, with
# the exception of the "meta.analysis" function.
sourceLines(orig_source2, 1, 338)
sourceLines(orig_source2, 409, 426)

# Create a customised version of the function meta.analysis, to correct an
# issue with a path variable that doesn't exist, correct a difference in file
# names between the code and the shared data files, and also to return a
# meta-analysis model object.

# Read in the entire source of the "functions" code file.
temp_code <- readLines(con = orig_source2)

# Extract the code for the meta.analysis function.
temp_mafn <- temp_code[340:407]

# Update the line of code which refers to "main.directory" to fix the folder
# location, and also rename the file.
temp_mafn[4] <- sub(pattern = "main.directory",
                    replacement = "\"original\"",
                    x = temp_mafn[4],
                    fixed = TRUE)
temp_mafn[4] <- sub(pattern = "Dataset info.csv",
                    replacement = "Dataset_info.csv",
                    x = temp_mafn[4],
                    fixed = TRUE)

# Update the line of code which prints the model object (in the case of no
# moderators) to instead return the model object when there are 3 moderators.
temp_mafn[34] <- sub(pattern = "if(length(moderators) == 0) print(x0)",
                     replacement = "if(length(moderators) == 3) return(x0)",
                     x = temp_mafn[34],
                     fixed = TRUE)

# Write the updated function to a temporary file.
cat(temp_mafn, file = "MA147_temp_function.R", sep = "\n")

# Read in the function that was just written.
sourceLines("MA147_temp_function.R", 1, 68)

# Run the meta-analysis for the condition "Varying N" when the fitness exponent
# is 1.0, and Ne is set to 10, and with no moderators.
# Custom code is required because the analysis code calls the meta.analysis
# function without directing the output to an object in the environment (the
# original function essentially just printed to console/plots).
x0_result <- meta.analysis(varyingN[varyingN$Fitness.exponent == 1, ],
                           "Rel.fitness.polyandry",
                           "N",
                           10,
                           moderators = c("sex", "taxon", "trait.type"))

repro_result_df <- data.frame(ID = "MA147",
                             source = "repro",
                             result_type = "mean",
                             es_type = "percentage",
                             point_est = round(x0_result$b, 2),
                             se = round(x0_result$se, 3),
                             ci_lower = round(x0_result$ci.lb, 3),
                             ci_upper = round(x0_result$ci.ub, 2),
                             n = x0_result$k)
rownames(repro_result_df) <- NULL

knitr::kable(x = repro_result_df)

```

# Compare original and reproduced result
```{r compare}

result_compare <- compare_vars(df_orig = orig_result_df,
                                df_repro = repro_result_df,
                                checkvars = c("point_est", "se",
                                              "ci_lower", "ci_upper",
                                              "n"))

knitr::kable(x = orig_result_df[, c("ID", "result_type", "es_type")],
             caption = "Details of result")

knitr::kable(x = result_compare,
             caption = "Comparison of original and reproduced values")

# Write results comparison to file.
out1 <- orig_result_df[1, c("ID", "result_type", "es_type")]
out2 <- cbind(out1, result_compare, row.names = NULL)
write.csv(x = out2, file = here::here("output", "MA147_result_comparison.csv"),
          row.names = FALSE)

```

# R session information

```{r rsession}
devtools::session_info()
```
