---
title: "Reproducibility Report for MA188"
author: "Steven Kambouris"
date: "18/09/2021"
output: html_document
knit: (function(input, ...){
    rmarkdown::render(input, output_dir = here::here("output"), envir = globalenv())
  })
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      include = TRUE)
```

# Reproducing result from

Senior, A. M., Nakagawa, S., Lihoreau, M., Simpson, S. J., & Raubenheimer, D. (2015). An Overlooked Consequence of Dietary Mixing: A Varied Diet Reduces Interindividual Variance in Fitness. _The American Naturalist_, _186_(5), 649–659. https://doi.org/10.1086/683182

# Result to be reproduced

> REMA of lnRR estimated a negative statistically significant effect (REMA est., CI for lnRR = -0.363, -0.408 to -0.318; fig. 2), which exponentiates to a ratio of mean of fitness-related traits on single-food diets to mixed diets of 0.700; that is, mean fitness is 30% lower on single foods. (Senior et al., 2015, p.653)

Earlier on p.653, the article states that there were 818 estimates of lnRR, so the sample size is 818.

```{r orig-result}
orig_result_df <- data.frame(ID = "MA188",
                             source = "original",
                             result_type = "mean",
                             es_type = "Log response ratio",
                             point_est = -0.363,
                             ci_lower = -0.408,
                             ci_upper = -0.318,
                             n = 818)

knitr::kable(x = orig_result_df)
```

# Details of shared data and code files

The following data and code files were shared on Dryad:

Senior, A. M., Nakagawa, S., Lihoreau, M., Simpson, S. J., & Raubenheimer, D. (2015). _Data from: An overlooked consequence of dietary mixing: A varied diet reduces interindividual variance in fitness._ Dryad Digital Repository. https://doi.org/10.5061/dryad.9hc76

* Code.R
* Data.Objects.Rdata

These files are licensed under a [CC0 1.0 Universal (CC0 1.0) Public Domain Dedication](https://creativecommons.org/publicdomain/zero/1.0/) license.

# Applicability of shared data and code files

## Data
The usage notes on the Dryad repository web page make things very clear: there is only one data file (`Data.Objects.Rdata`) which contains all data relevant to the article analyses. Further, the usage notes mention that the code file `Code.R` contains comments/instructions about accessing the data. The code file does contain a codebook describing all the components within the data file, as well as an additional codebook describing the columns found in the "main" data component `Effect.Sizes`.

## Code
The usage notes on the Dryad repository web page are very straightforward: the file `Code.R` contains all code to recreate the analyses in the article. The code file is extensively documented throughout with comments which makes identifying the relevant sections of code to execute straightforward.

# Set up
```{r library}

# Load packages required for working with original files.
library(here)

# Load custom package for (i) running the source command for specific line
# numbers within a file and (ii) for calculating the percentage error between
# the original and reproduced values.
library(reprohelper)

# Load packages required for data import/cleaning.
# (None required.)

# Load packages required by the code to run.
# (These packages are loaded in the same order as loaded in the original code
# file.)
library("metafor")
library("MCMCglmm")

# Set the path to the original code file(s).
orig_source <- here::here("original", "Code.R")
```

# Import and clean data
```{r importdata}

load(here::here("original", "Data.Objects.Rdata"))

```

# (Re-)run the analysis to reproduce result
```{r analysis}

# Fit random-effects meta-analysis (REMA) model for the difference in mean
# fitness.
sourceLines(orig_source, 53, 60)

#model_summary <- summary(REMA.lnRR)

repro_result_df <- data.frame(ID = "MA188",
                             source = "repro",
                             result_type = "mean",
                             es_type = "log response ratio",
                             point_est = round(REMA.lnRR$beta, 3),
                             ci_lower = round(REMA.lnRR$ci.lb, 3),
                             ci_upper = round(REMA.lnRR$ci.ub, 3),
                             n = REMA.lnRR$k)
rownames(repro_result_df) <- NULL

knitr::kable(x = repro_result_df)

```

# Compare original and reproduced result
```{r compare}

result_compare <- compare_vars(df_orig = orig_result_df,
                                df_repro = repro_result_df,
                                checkvars = c("point_est",
                                              "ci_lower", "ci_upper",
                                              "n"))

knitr::kable(x = orig_result_df[, c("ID", "result_type", "es_type")],
             caption = "Details of result")

knitr::kable(x = result_compare,
             caption = "Comparison of original and reproduced values")

# Write results comparison to file.
out1 <- orig_result_df[1, c("ID", "result_type", "es_type")]
out2 <- cbind(out1, result_compare, row.names = NULL)
write.csv(x = out2, file = here::here("output", "MA188_result_comparison.csv"),
          row.names = FALSE)

```

# R session information

```{r rsession}
devtools::session_info()
```
