---
title: "Reproducibility Report for MA081"
author: "Steven Kambouris"
date: "21/06/2022"
output: html_document
knit: (function(input, ...){
    rmarkdown::render(input, output_dir = here::here("output"), envir = globalenv())
  })
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      include = TRUE)
```

# Reproducing result from

Jaffé, R., Pope, N., Acosta, A. L., Alves, D. A., Arias, M. C., De la Rúa, P., Francisco, F. O., Giannini, T. C., González‐Chaves, A., Imperatriz‐Fonseca, V. L., Tavares, M. G., Jha, S., & Carvalheiro, L. G. (2016). Beekeeping practices and geographic distance, not land use, drive gene flow across tropical bees. _Molecular Ecology_, _25_(21), 5345–5358. https://doi.org/10.1111/mec.13852

# Result to be reproduced

> As expected, genetic differentiation was explained by geographic distance across the 17 analysed stingless bee species (Fig. 1, Table 2)... Mean IBD [isolation by geographic distance] slope overall species was 1.30 (95% CI: 0.95–1.66)... (Jaffé et al., 2016, p.5351)

Table 2 (p.5352) in the article shows that the sample size associated with the mean slope was 1296, which is the number of model slope parameters that were averaged.

```{r orig-result}
orig_result_df <- data.frame(ID = "MA081",
                             source = "original",
                             result_type = "mean",
                             es_type = "slope parameter",
                             point_est = 1.30,
                             ci_lower = 0.95,
                             ci_upper = 1.66,
                             n = 1296)

knitr::kable(x = orig_result_df)
```

# Details of shared data and code files

The following data and code files were shared as supporting information on the web page for the article (https://onlinelibrary.wiley.com/doi/full/10.1111/mec.13852):

* mec13852-sup-0006-DataS1.zip
    + DMA_rd_roads.csv
    + DMA-May2015.csv
    + corMLPE.R
    + Full_Script.R
    + mavg.R
    + MLPElikelihood_take2.cpp

There is no licencing information available for these files.

# Applicability of shared data and code files

## Data
The data archive (described on the journal article webpage as "Full dataset and R scripts") contains only two data files, `DMA_rd_roads.csv` and `DMA-May2015.csv`. These two files are imported by the R script `Full_Script.R` (see below).

## Code
There are three R scripts and one C++ script in the archive. In the absence of a readme file or other documentation, the name of the file `Full_Script.R` was the best clue about how to proceed. This code file imports the two included data files by name, and invokes the other included R scripts and C++ script. The comments in this file provided some clues about how to run the analysis to reproduce the selected result.

# Set up
```{r library}
# Load packages required for working with original files.
library(here)

# Load custom package for (i) running the source command for specific line
# numbers within a file and (ii) for calculating the percentage error between
# the original and reproduced values.
library(reprohelper)

# Load packages required for data import/cleaning.
# (None required.)

# Load packages required by the code to run.
# (These packages are loaded in the same order as loaded in the original code
# file.)

# From Full_Script.R
library(lme4)
library(MuMIn)
library(ggplot2)
library(Rcpp)

# From corMLPE.R
library(nlme)
library(plyr)
library(Matrix)

# Set the path to the original code file(s).
orig_source <- here::here("original", "Full_Script.R")
orig_source2 <- here::here("original", "corMLPE.R")
orig_source3 <- here::here("original", "mavg.R")
orig_source4 <- here::here("original", "MLPElikelihood_take2.cpp")

```

# Import and clean data
```{r importdata}

DMA <- read.csv(here::here("original", "DMA-May2015.csv"), header=T)


# Perform some custom cleaning - when the files are imported as-is, the check on
# lines 24-25 checking the "alignment" of the DMA and Road datasets fails.
# The issue seems to be the inconsistent name of a value in the Pop1 variable
# in the Road data: there is both a value "Manaus_M. Pascoal" and
# "Manaus_M._Pascoal"; the DMA data just has "Manaus_M._Pascoal". Solution is to
# make the change in the Road data before converting Pop1 to a factor. Then, all
# the factor labels will align correctly.

# Import the roads data with stringsAsFactors = FALSE.
Road <- read.csv(here::here("original", "DMA_rd_roads.csv"), stringsAsFactors = FALSE)

# Correct the errant value of Pop1.
Road[Road$Pop1 == "Manaus_M. Pascoal", "Pop1"] <- "Manaus_M._Pascoal"

# Convert all the string variables to factors.
Road$Species <- factor(Road$Species)
Road$Pop1 <- factor(Road$Pop1)
Road$Pop2 <- factor(Road$Pop2)
Road$Managed <- factor(Road$Managed)

```

# (Re-)run the analysis to reproduce result
```{r analysis}

# Format DMA data.
sourceLines(orig_source, 12, 14)

# Format Roads data.
sourceLines(orig_source, 18, 21)

# Check that the DMA and Roads data are aligned.
sourceLines(orig_source, 23, 25)

# Perform additional data transformations.
sourceLines(orig_source, 27, 46)

# Run corMLPE.R (loads a bunch of functions)
sourceLines(orig_source2, 39, 384)

# Run C++ code
# Change to original line required due to path.
sourceCpp(orig_source4)

# Re-order DMA data, fit the full model.
sourceLines(orig_source, 56, 64)

# Get covariate and Z matrices, re-fit full model.
sourceLines(orig_source, 68, 78)

# Perform "model fitting" according to the comment in source file.
sourceLines(orig_source, 82, 87)

# 2022-06-21: New stuff follows here.

# This is the point at which things can't be replicated.
#
# mavg.R is supposed to create a script, bootstrap.R, which runs the
# bootstrap simulations used to calculate confidence intervals.
#
# However, attempting to run the bootstrapping functions results in an
# error:
# Error in solve.default(-val) : 
#   Lapack routine dgesv: system is exactly singular: U[3,3] = 0
#
# This error comes from the solve() function in base R, which is invoked when
# attempting to update a linear mixed model (lme object from package nlme).
#
# The following code is the minimum required to reproduce the issue:
# ******************************************************************
# # Load the functions defined in mavg.R.
# sourceLines(orig_source3, 1, 140)
#
# # Generate a set of 1000 random seeds to use for bootstrapping.
# sourceLines(orig_source3, 142, 142)
# set.seed(100081)
# sourceLines(orig_source3, 145, 145)
#
# # Generate fitted values, according to mavg.R.
# sourceLines(orig_source3, 149, 150)
#
# # Re-run corMLPE.R and the C++ code, as according to mavg.R.
# sourceLines(orig_source2, 39, 384)
# sourceCpp(orig_source4)
#
# # Calculate the yhat and shat objects.
# sourceLines(orig_source3, 156, 161)
#
# # Custom code: minimum code to attempt bootstrapping:
# for (j in 1:1000) {
#   cat(paste0(Sys.time(), ": j = ", j, "\n"))
#   bootstrapConditional(yhat, shat, model.list, seed.list, j)
# }
# ******************************************************************
# 
# The code above will result in the singular matrix error during
# the execution of bootstrapConditional for j = 2 (i.e. the second seed).
#
# It's unclear what the problem is - the original code doesn't specify what
# to do if one simulation fails (try another seed until the calculation
# succeeds, until one reaches 1000? Ignore failures and calculate bootstrapped
# results based on less than 1000 simulated data points?)
#
# Additionally, the shared code is incomplete: code which compiles the separate
# <slopes|intercepts|fitted|fixed>_conditional_<j>.tab files into a single file
# which is imported by Full_Script.R as SLOPES_CONDITIONAL.TAB, etc. isn't
# included, even though it would be a relatively trivial to combine the files.
#
# As a result of all this, only a partial reproduction of results can
# continue - the confidence interval (which relies on bootstrapping) cannot be
# calculated, but the overall mean and number of the IBD slope parameters
# can still be.

# Load the `fix` function from mavg.R.
sourceLines(orig_source3, 44, 61)

# The IBD slope is a fixed effect in these models, named "Rnull.t".
# Use the fix function to calculate model-averaged fixed effects, as used in
# the script Full_Script.R at line 173. Custom code is needed because the
# original code embeds this calculation in a call to calculate confidence
# intervals.
model_avg_fixed <- fix(parm)

repro_result_df <- data.frame(ID = "MA081",
                             source = "repro",
                             result_type = "mean",
                             es_type = "slope parameter",
                             point_est = round(model_avg_fixed["Rnull.t"], 2),
                             ci_lower = NA_real_,
                             ci_upper = NA_real_,
                             n = length(parm))
rownames(repro_result_df) <- NULL

knitr::kable(x = repro_result_df)

```

# Compare original and reproduced result
```{r compare}

result_compare <- compare_vars(df_orig = orig_result_df,
                                df_repro = repro_result_df,
                                checkvars = c("point_est", "ci_lower",
                                              "ci_upper", "n"))

knitr::kable(x = orig_result_df[, c("ID", "result_type", "es_type")],
             caption = "Details of result")

knitr::kable(x = result_compare,
             caption = "Comparison of original and reproduced values")

# Write results comparison to file.
out1 <- orig_result_df[1, c("ID", "result_type", "es_type")]
out2 <- cbind(out1, result_compare, row.names = NULL)
write.csv(x = out2, file = here::here("output", "MA081_result_comparison.csv"),
          row.names = FALSE)

```

# R session information

```{r rsession}
devtools::session_info()
```
