---
title: "Reproducibility Report for MA016"
author: "Steven Kambouris"
date: "18/09/2021"
output: html_document
knit: (function(input, ...){
    rmarkdown::render(input, output_dir = here::here("output"), envir = globalenv())
  })
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      include = TRUE)
```

# Reproducing result from

Xu, X., Medvigy, D., Joseph Wright, S., Kitajima, K., Wu, J., Albert, L. P., Martins, G. A., Saleska, S. R., & Pacala, S. W. (2017). Variations of leaf longevity in tropical moist forests predicted by a trait-driven carbon optimality model. _Ecology Letters_, _20_(9), 1097–1106. https://doi.org/10.1111/ele.12804

# Result to be reproduced

> Our meta-analysis shows that the parameter $b$ (the inverse of leaf ageing rate) varies by two orders of magnitude (Fig. 2), ranging from 36 to 4509 days. Over all species, $b$ is negatively correlated with mass-based photosynthetic capacity,
$\overline{Vcmax25_{m}}$ ($r = -0.83$, $P \ll 0.001$). (Xu et al., 2017, p.1100)

The sample size is not mentioned here, but in the Material and Methods section, the authors write regarding the meta-analysis data: "In total, we compiled a dataset including 19 temperate and 30 tropical species (Appendix S2)." (Xu et al., 2017, p.1099). This implies a sample size of 49.

```{r orig-result}
orig_result_df <- data.frame(ID = "MA016",
                             source = "original",
                             result_type = "correlation",
                             es_type = "Pearson's r",
                             point_est = -0.83,
                             p_value = 0.001,
                             n = 49)

knitr::kable(x = orig_result_df)
```

# Details of shared data and code files

The following data and code files were shared as supporting information on the web page for the article (https://onlinelibrary.wiley.com/doi/full/10.1111/ele.12804):

* ele12804-sup-0001-FigS1-S8.docx
* ele12804-sup-0002-AppendixS1.docx
* ele12804-sup-0003-AppendixA2.xlsx
* ele12804-sup-0004-appendixs3.xlsx
* ele12804-sup-0005-appendixs4.rar
    + BCI_LL_sensitivity.py
    + BCI_LL_simulation.py
    + Calculate_Vcmax25.py
    + myForest.py
    + ReadMe.txt

There is no licencing information available for these files.

# Applicability of shared data and code files

## Data

The article mentions that the data collected for the meta-analysis is in Appendix S2, which would correspond to file ele12804-sup-0003-AppendixA2.xlsx. This file contains columns named "b" and "Vcmax25_mass_mature", which match up with what is mentioned in the article.

All values of "Vcmax25_mass_mature" (and some values of "b") are defined by worksheet formulas instead of being static values, and are calculated from various other values reported in the original studies. These calculations are explained in Appendix S1 (file ele12804-sup-0002-AppendixS1.docx).

**There are data files applicable to reproducing the selected result:**

* **ele12804-sup-0003-AppendixA2.xlsx**

## Code

File ReadMe.txt describes the function of all Python code files. These code files are applicable to the numerical experiments/simulations performed in the article, and are not relevant to the calculation of results related to the meta-analysis.

**There are no code files applicable to reproducing the selected result.**

**This means that the reproduction of results can't proceed via the re-running of code, but completely new code will need to be written to attempt to reproduce the result.**

# Set up

```{r library}
# Load packages required for working with original files.
library(here)

# Load custom package for (i) running the source command for specific line
# numbers within a file and (ii) for calculating the percentage error between
# the original and reproduced values.
library(reprohelper)

# Load packages required for data import/cleaning.
library(openxlsx)

# Load packages required by the code to run.
# (none required)

```

# Import and clean data
```{r importdata}
raw_data <- read.xlsx(xlsxFile = here("original",
                                      "ele12804-sup-0003-appendixa2.xlsx"),
                      sheet = "Data",
                      colNames = TRUE,
                      rows = c(1, 3:51))

clean_data <- raw_data
```

# (Re-)run the analysis to reproduce result
```{r analysis}
# Start with a naive correlation between b and Vcmax25 (mass).
# In the absence of other information, assuming a two-sided test.
corr_result <- cor.test(x = clean_data$Vcmax25_mass_mature,
                        y = clean_data$b,
                        alternative = "two.sided",
                        method = "pearson",
                        conf.level = 0.95)

# This isn't the same as what was reported. But, the mention of the orders of magnitude that b varies over, plus the use of the log scale on both axes of Figure 2 in the article (which plots Vcmax25 (mass) by b), indicates that the values should be log-transformed first.
corr_result_log <- cor.test(x = log10(clean_data$Vcmax25_mass_mature),
                        y = log10(clean_data$b),
                        alternative = "two.sided",
                        method = "pearson",
                        conf.level = 0.95)

repro_result_df <- data.frame(ID = "MA016",
                             source = "repro",
                             result_type = "correlation",
                             es_type = "Pearson's r",
                             point_est = round(corr_result_log$estimate, 2),
                             p_value = corr_result_log$p.value,
                             n = nrow(clean_data))
rownames(repro_result_df) <- NULL

knitr::kable(x = repro_result_df)

```

# Compare original and reproduced result
```{r compare}

result_compare <- compare_vars(df_orig = orig_result_df,
                                df_repro = repro_result_df,
                                checkvars = c("point_est", "p_value", "n"))

knitr::kable(x = orig_result_df[, c("ID", "result_type", "es_type")],
             caption = "Details of result")

knitr::kable(x = result_compare,
             caption = "Comparison of original and reproduced values")

# Write results comparison to file.
out1 <- orig_result_df[1, c("ID", "result_type", "es_type")]
out2 <- cbind(out1, result_compare, row.names = NULL)
write.csv(x = out2, file = here::here("output", "MA016_result_comparison.csv"),
          row.names = FALSE)

```

# R session information

```{r rsession}
devtools::session_info()
```
