---
title: "Reproducibility Report for MA145"
author: "Steven Kambouris"
date: "18/09/2021"
output: html_document
knit: (function(input, ...){
    rmarkdown::render(input, output_dir = here::here("output"), envir = globalenv())
  })
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      include = TRUE)
```

# Reproducing result from

Moore, F. R., Shuker, D. M., & Dougherty, L. (2016). Stress and sexual signaling: A systematic review and meta-analysis. _Behavioral Ecology_, _27_(2), 363–371. https://doi.org/10.1093/beheco/arv195

# Result to be reproduced

> Across all effect sizes there was no significant correlation between stress levels and the degree of secondary sexual signaling (intercept-only MCMCglmm; posterior mean = −0.08, LHPD = −0.22, UHPD = 0.03, $k = 118$, $N_{studies}  = 38$, $N_{species}  = 25$). (Moore et al., 2016, p.366)

```{r orig-result}
orig_result_df <- data.frame(ID = "MA145",
                             source = "original",
                             result_type = "mean",
                             es_type = "Fisher z-transformation of correlation",
                             point_est = -0.08,
                             hpdi_lower = -0.22,
                             hpdi_upper = 0.03,
                             n = 118,
                             n_studies = 38,
                             n_species = 25)

knitr::kable(x = orig_result_df)
```

# Details of shared data and code files

The following data and code files were shared as supporting information on the web page for the article (https://academic.oup.com/beheco/article/27/2/363/2196777#supplementary-data):

* arv195_supplementary_data.zip
    + Supplementary_material.docx

There is no licencing information available for these files.

# Applicability of shared data and code files

## Data
The supplementary material consists of a single Microsoft Word document - not a traditional data file format. Inspection of the document revealed that the effect size data used in the meta-analysis was included as a table in the document, in Section 2, "Effect sizes used in final analysis". To be usable, this data would need to be extracted and formatted into a usable state.

The analysis code (see below) imports a phylogenetic tree data file, `all_species_cladogram.txt`. This data file isn't included in the supplementary material. However, the article includes a diagram of the relevant phylogenetic tree (Figure 2 on page 366), and the article states that all branch lengths were set to one. Therefore, the data file could be reconstructed (in Newick/New Hampshire tree format) from the diagram and branch length information. My reconstruction of the data file (`MA145_recreated_all_species_cladogram.txt`) has been included here in order to run the analysis.

## Code
The supplementary material consists of a single Microsoft Word document - not a traditional code file format. Inspection of the document revealed that the code used to conduct the meta-analysis was included in the document, in Section 4, "R code used for analysis". To be usable, this code would need to be extracted and placed into a standard text file.

# Set up
```{r library}

# Load packages required for working with original files.
library(here)

# Load custom package for (i) running the source command for specific line
# numbers within a file and (ii) for calculating the percentage error between
# the original and reproduced values.
library(reprohelper)

# Load packages required for data import/cleaning.
library(docxtractr)
library(officer)

# The analysis code is "trapped" in the shared supplementary material Word
# document, it needs to be extracted and saved to a text file.

# Import the word document using the officer read_docx function.
word_doc1 <- officer::read_docx(here::here("original",
                                           "Supplementary_material.docx"))

# Summarise the imported Word document, creating a data frame.
word_sum1 <- officer::docx_summary(word_doc1)

# Extract the paragraphs in the Word document that correspond to the analysis
# code.
word_code1 <- word_sum1[word_sum1$doc_index %in% 118:337, "text"]

# Write the extracted code to a separate R script file which can then be
# referred to as a source.
# Write to the current working directory, which is where the session has write
# permission.
cat(word_code1, file = "MA145_code_extracted.R", sep = "\n")

# Clean up the objects created so they don't cause conflicts.
rm(list = c("word_doc1", "word_sum1", "word_code1"))

# Load packages required by the code to run.
# (These packages are loaded in the same order as loaded in the original code
# file.)
library(ape) 
library(MCMCglmm)
library(orthopolynom)
library(metafor)

# Set the path to the extracted code file, which is being treated as the
# "original" code, despite the extraction step.
orig_source <- here::here("MA145_code_extracted.R")
```

# Import and clean data
```{r importdata}

# The effect size data used in the meta-analysis is "trapped" in a table within
# the shared supplementary material Word document. It needs to be extracted and
# formatted into a useable form.

# Read in the Word document using the docxtractr package this time.
Word_doc <- docxtractr::read_docx(here::here("original",
                                             "Supplementary_material.docx"))

# Identify and extract the table containing the effect sizes. It is the table
# with index 3 in the document.
print(docxtractr::docx_tbl_count(Word_doc))
print(docxtractr::docx_describe_tbls(Word_doc))
Word_table <- docxtractr::docx_extract_tbl(Word_doc, 3)

# Problem: many cells in the table were merged, and values in merged cells were
# separated by line breaks, which have been removed by the import process.
# Need to restore the line-break separated values to the appropriate row in the
# data table.
Word_table_cleaned <- Word_table


# Drop rows that contain only class/order information, convert these to columns
# instead.
Word_table_cleaned$class <- ""
Word_table_cleaned$order <- ""
Word_table_cleaned[1:16, "class"] <- "Amphibian"
Word_table_cleaned[1:16, "order"] <- "Salientia"
Word_table_cleaned[17:94, "class"] <- "Avian"
Word_table_cleaned[17:35, "order"] <- "Galliforme"
Word_table_cleaned[36:94, "order"] <- "Passeriforme"
Word_table_cleaned[95:103, "class"] <- "Mammalian"
Word_table_cleaned[95:103, "order"] <- "Primate"
Word_table_cleaned[104:121, "class"] <- "Reptilian"
Word_table_cleaned[104:121, "order"] <- "Squamata"

# Get the rows which do not contain the class/order information in the Species
# column - those are empty subheader rows.
non_subheader_rows <- which(!Word_table_cleaned$Species %in% c("Amphibian",
                                                               "Salientia",
                                                               "Avian",
                                                               "Galliforme",
                                                               "Passeriforme",
                                                               "Mammalian",
                                                               "Primate",
                                                               "ReptilianSquamata"))
Word_table_cleaned <- Word_table_cleaned[non_subheader_rows, ]

# Clean Species.
check_species <- unique(Word_table_cleaned$Species)

Word_table_cleaned[Word_table_cleaned$Species == check_species[3],
                   "Species"] <- "Great plains toad (Bufo cognatus)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[5],
                   "Species"] <- "Smith frog (Hypiboas faber)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[6],
                   "Species"] <- "Green tree frog (Litoria caerulea)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[7],
                   "Species"] <- "Red legged partridge (Alectoris rufa)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[9],
                   "Species"] <- "Grey partridge (Perdix perdix)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[10],
                   "Species"] <- "Red junglefowl (Gallus gallus)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[11],
                   "Species"] <- "Red grouse (Lagopus lagopus scoticus)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[12],
                   "Species"] <- "Northern cardinal (Cardinalis cardinalis)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[14],
                   "Species"] <- "House finch (Carpodacus mexicanus)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[15],
                   "Species"] <- "Red bishop (Euplectes orix)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[16],
                   "Species"] <- "Collared flycatcher (Ficedula albicollis)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[17],
                   "Species"] <- "Pied flycatcher (Ficedula hypoleuca)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[18],
                   "Species"] <- "Barn swallow (Hirundo rusitca)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[19],
                   "Species"] <- "Red backed fairy wren (Malarus melodicus)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[20],
                   "Species"] <- "Song sparrow (Melospiza melodia)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[22],
                   "Species"] <- "Blue tit (Parus caeruleus)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[24],
                   "Species"] <- "Human (Homo sapien)"
Word_table_cleaned[Word_table_cleaned$Species == check_species[28],
                   "Species"] <- "Striped plateau lizard (Sceloporus virgatus)"

# Fill in missing species values.
for (i in 2:114) {
  if (Word_table_cleaned$Species[i] == "") {
    Word_table_cleaned$Species[i] <- Word_table_cleaned$Species[i - 1]
  }
}

# Duplicate some doubled-up rows.
# Row 94 is doubled up.
dupl_row94 <- Word_table_cleaned[94, ]

# Row 112 is doubled up.
dupl_row112 <- Word_table_cleaned[112, ]

# Row 113 is quadrupled up.
dupl_row113 <- Word_table_cleaned[113, ]

# Drop the empty row at the end.
Word_table_cleaned <- Word_table_cleaned[1:113, ]

# Add Row 112 once, and 113 four times to the end of rows 1:112.
Word_table_cleaned <- rbind(Word_table_cleaned[1:112, ],
                            dupl_row112,
                            dupl_row113, dupl_row113, dupl_row113, dupl_row113)

# Add Row 94 once, in the correct location.
Word_table_cleaned <- rbind(Word_table_cleaned[1:94, ],
                            dupl_row94,
                            Word_table_cleaned[95:117, ])

# Clean trait.
Word_table_cleaned[1:4, "Trait"] <- "Adoption of calling strategy"
Word_table_cleaned[24:28, "Trait"] <- "Comb length"
Word_table_cleaned[42:44, "Trait"] <- Word_table_cleaned[42, "Trait"]
Word_table_cleaned[42:44, "Trait"] <- Word_table_cleaned[42, "Trait"]
Word_table_cleaned[45:47, "Trait"] <- Word_table_cleaned[45, "Trait"]
Word_table_cleaned[48:50, "Trait"] <- Word_table_cleaned[48, "Trait"]
Word_table_cleaned[51:53, "Trait"] <- Word_table_cleaned[51, "Trait"]
Word_table_cleaned[54:56, "Trait"] <- Word_table_cleaned[54, "Trait"]
Word_table_cleaned[59:61, "Trait"] <- "Brightness of ventral phaeomelanic plumage"
Word_table_cleaned[63:64, "Trait"] <- "Red and black plumage coverage"
Word_table_cleaned[80:83, "Trait"] <- "Chroma of yellow plumage"
Word_table_cleaned[90:94, "Trait"] <- "Female preference for male faces"
Word_table_cleaned[95, "Trait"] <- "Male preference for female faces"
Word_table_cleaned[113, "Trait"] <- "Size of orange ovulatory throat patch"
Word_table_cleaned[114, "Trait"] <- "Orange colouration of throat patch (principal component)"
Word_table_cleaned[115, "Trait"] <- "Size of orange ovulatory throat patch"
Word_table_cleaned[116, "Trait"] <- "Mean reflectance of throat patch"
Word_table_cleaned[117, "Trait"] <- "Orange colouration of throat patch (principal component 1)"
Word_table_cleaned[118, "Trait"] <- "Orange colouration of throat patch (principal component 2)"

# Clean Sex.
Word_table_cleaned[1:9, "Sex"] <- "M"
Word_table_cleaned[11:17, "Sex"] <- "M"
Word_table_cleaned[18, "Sex"] <- "F"
Word_table_cleaned[21:33, "Sex"] <- "M"
Word_table_cleaned[34:35, "Sex"] <- "F"
Word_table_cleaned[37:61, "Sex"] <- "M"
Word_table_cleaned[63:78, "Sex"] <- "M"
Word_table_cleaned[90:94, "Sex"] <- "M"
Word_table_cleaned[95, "Sex"] <- "F"
Word_table_cleaned[98:112, "Sex"] <- "M"
Word_table_cleaned[113:118, "Sex"] <- "F"

# Clean N.
Word_table_cleaned[11:12, "N"] <- "29"
Word_table_cleaned[13:14, "N"] <- "68"
Word_table_cleaned[15, "N"] <- "30"
Word_table_cleaned[16, "N"] <- "29"
Word_table_cleaned[17, "N"] <- "30"
Word_table_cleaned[18, "N"] <- "20"
Word_table_cleaned[21:23, "N"] <- "48"
Word_table_cleaned[37:39, "N"] <- "31"
Word_table_cleaned[40:41, "N"] <- "52"
Word_table_cleaned[42:56, "N"] <- "23"
Word_table_cleaned[59:61, "N"] <- "90"
Word_table_cleaned[74:77, "N"] <- "24"
Word_table_cleaned[94, "N"] <- "74"
Word_table_cleaned[95, "N"] <- "52"
Word_table_cleaned[99:106, "N"] <- "31"
Word_table_cleaned[107:112, "N"] <- "29"
Word_table_cleaned[113:118, "N"] <- "45"

# Clean Stress.measure.
Word_table_cleaned[1:2, "Stress.measure"] <- "BCORT"
Word_table_cleaned[3:4, "Stress.measure"] <- "ECORT"
Word_table_cleaned[11:12, "Stress.measure"] <- "BCORT"
Word_table_cleaned[13:14, "Stress.measure"] <- "ECORT"
Word_table_cleaned[15:18, "Stress.measure"] <- "H:L"
Word_table_cleaned[24:28, "Stress.measure"] <- "BCORT"
Word_table_cleaned[29:31, "Stress.measure"] <- "FeathCORT"
Word_table_cleaned[32:35, "Stress.measure"] <- "H:L"
Word_table_cleaned[37:39, "Stress.measure"] <- "FeathCORT"
Word_table_cleaned[40:41, "Stress.measure"] <- "H:L"
Word_table_cleaned[57:58, "Stress.measure"] <- "FecCORT"
Word_table_cleaned[65:67, "Stress.measure"] <- "BCORT"
Word_table_cleaned[68:70, "Stress.measure"] <- "PCORT"
Word_table_cleaned[71:73, "Stress.measure"] <- "PCORT-BCORT"
Word_table_cleaned[74:75, "Stress.measure"] <- "BCORT"
Word_table_cleaned[76:77, "Stress.measure"] <- "PCORT"
Word_table_cleaned[90:95, "Stress.measure"] <- "BCORT"
Word_table_cleaned[113:114, "Stress.measure"] <- "BCORT"
Word_table_cleaned[115:118, "Stress.measure"] <- "ECORT"

# Clean Covariates.
Word_table_cleaned[32:35, "Covariates"] <- "Date and time"
Word_table_cleaned[37:39, "Covariates"] <- "Body size"
Word_table_cleaned[57:58, "Covariates"] <- "Date of arrival at breeding grounds body condition HSP60 age"
Word_table_cleaned[59:61, "Covariates"] <- "Site date body mass timing of sunset"
Word_table_cleaned[63:64, "Covariates"] <- "Date and testosterone"
Word_table_cleaned[90, "Covariates"] <- ""
Word_table_cleaned[92:93, "Covariates"] <- "Testosterone"
Word_table_cleaned[107:112, "Covariates"] <- "Moult status colour alleles and number of ingested larvae"
Word_table_cleaned[113:114, "Covariates"] <- "Estradial progesterone testosterone"
Word_table_cleaned[115:118, "Covariates"] <- "Body mass reproductive state"

# Clean df.
Word_table_cleaned[13:14, "df"] <- "68"
Word_table_cleaned[15, "df"] <- "29"
Word_table_cleaned[16, "df"] <- "28"
Word_table_cleaned[17, "df"] <- "29"
Word_table_cleaned[18, "df"] <- "19"
Word_table_cleaned[21:23, "df"] <- "43"
Word_table_cleaned[37:39, "df"] <- "30"
Word_table_cleaned[40:41, "df"] <- "40"
Word_table_cleaned[42:56, "df"] <- "23"
Word_table_cleaned[59:61, "df"] <- "87"
Word_table_cleaned[74:77, "df"] <- "24"
Word_table_cleaned[99:106, "df"] <- "30"
Word_table_cleaned[107:112, "df"] <- "28"
Word_table_cleaned[94, "df"] <- "73"
Word_table_cleaned[95, "df"] <- "52"
Word_table_cleaned[113:114, "df"] <- "45"
Word_table_cleaned[115:118, "df"] <- "42"

# Clean Zr.
Word_table_cleaned[94, "Zr"] <- "-0.172"
Word_table_cleaned[95, "Zr"] <- "-0.405"
Word_table_cleaned[113, "Zr"] <- "-0.427"
Word_table_cleaned[114, "Zr"] <- "-0.47"
Word_table_cleaned[115, "Zr"] <- "-0.253"
Word_table_cleaned[116, "Zr"] <- "0.152"
Word_table_cleaned[117, "Zr"] <- "-0.134"
Word_table_cleaned[118, "Zr"] <- "-0.374"

# Clean var.
Word_table_cleaned[94, "var"] <- "0.014"
Word_table_cleaned[95, "var"] <- "0.02"
Word_table_cleaned[113:118, "var"] <- "0.024"

# Clean Study.
Word_table_cleaned[94, "Study"] <- "Rantala et al. 2012"
Word_table_cleaned[95, "Study"] <- "Rantala et al. 2013"
Word_table_cleaned[113:118, "Study"] <- "Weiss et al. 2013"

# Check for issues with double spacing, or other artifacts preventing the same
# study from having the same value.
check_study <- unique(Word_table_cleaned$Study)
print(length(check_study))

Word_table_cleaned[which(Word_table_cleaned$Study == "Perez-Rodriguez and  Viñuela 2008"),
                   "Study"] <- "Perez-Rodriguez and Viñuela 2008"

check_study <- unique(Word_table_cleaned$Study)
print(length(check_study))

# Convert the type of some columns.
Word_table_cleaned$N <- as.integer(Word_table_cleaned$N)
Word_table_cleaned$df <- as.integer(Word_table_cleaned$df)
Word_table_cleaned$Zr <- as.numeric(Word_table_cleaned$Zr)
Word_table_cleaned$var <- as.numeric(Word_table_cleaned$var)

# Recode the species names.
Word_table_cleaned[Word_table_cleaned$Species == "Great plains toad (Bufo cognatus)",
                   "Species"] <- "Bufo_cognatus"
Word_table_cleaned[Word_table_cleaned$Species == "Woodhouse’s toad (Bufo Woodhousii)",
                   "Species"] <- "Bufo_woodhousii"
Word_table_cleaned[Word_table_cleaned$Species == "Smith frog (Hypiboas faber)",
                   "Species"] <- "Hypsiboas_faber"
Word_table_cleaned[Word_table_cleaned$Species == "Green tree frog (Litoria caerulea)",
                   "Species"] <- "Litoria_caerulea"
Word_table_cleaned[Word_table_cleaned$Species == "Red legged partridge (Alectoris rufa)",
                   "Species"] <- "Alectoris_rufa"
Word_table_cleaned[Word_table_cleaned$Species == "Grey partridge (Perdix perdix)",
                   "Species"] <- "Perdix_perdix"
Word_table_cleaned[Word_table_cleaned$Species == "Red junglefowl (Gallus gallus)",
                   "Species"] <- "Gallus_gallus"
Word_table_cleaned[Word_table_cleaned$Species == "Red grouse (Lagopus lagopus scoticus)",
                   "Species"] <- "Lagopus_lagopus"
Word_table_cleaned[Word_table_cleaned$Species == "Northern cardinal (Cardinalis cardinalis)",
                   "Species"] <- "Cardinalis_cardinalis"
Word_table_cleaned[Word_table_cleaned$Species == "Greenfinch (Carduelis chloris)",
                   "Species"] <- "Carduelis_chloris"
Word_table_cleaned[Word_table_cleaned$Species == "House finch (Carpodacus mexicanus)",
                   "Species"] <- "Carpodacus_mexicanus"
Word_table_cleaned[Word_table_cleaned$Species == "Red bishop (Euplectes orix)",
                   "Species"] <- "Euplectes_orix"
Word_table_cleaned[Word_table_cleaned$Species == "Collared flycatcher (Ficedula albicollis)",
                   "Species"] <- "Ficedula_albicollis"
Word_table_cleaned[Word_table_cleaned$Species == "Pied flycatcher (Ficedula hypoleuca)",
                   "Species"] <- "Ficedula_hypoleuca"
Word_table_cleaned[Word_table_cleaned$Species == "Barn swallow (Hirundo rusitca)",
                   "Species"] <- "Hirundo_rustica"
Word_table_cleaned[Word_table_cleaned$Species == "Red backed fairy wren (Malarus melodicus)",
                   "Species"] <- "Malurus_melanocephalus"
Word_table_cleaned[Word_table_cleaned$Species == "Song sparrow (Melospiza melodia)",
                   "Species"] <- "Melospiza_melodia"
Word_table_cleaned[Word_table_cleaned$Species == "Brown headed cow bird (Molothrus ater)",
                   "Species"] <- "Molothrus_ater"
Word_table_cleaned[Word_table_cleaned$Species == "Blue tit (Parus caeruleus)",
                   "Species"] <- "Parus_caeruleus"
Word_table_cleaned[Word_table_cleaned$Species == "Red Winged blackbird (Agelaius phoeniceus)",
                   "Species"] <- "Agelaius_phoeniceus"
Word_table_cleaned[Word_table_cleaned$Species == "Human (Homo sapien)",
                   "Species"] <- "Homo_sapiens"
Word_table_cleaned[Word_table_cleaned$Species == "Mandrill (Madrillus sphinx)",
                   "Species"] <- "Mandrillus_sphinx"
Word_table_cleaned[Word_table_cleaned$Species == "Rock hyrax (Procavia capensis)",
                   "Species"] <- "Procavia_capensis"
Word_table_cleaned[Word_table_cleaned$Species == "Common lizard (Lacerta vivipara)",
                   "Species"] <- "Lacerta_vivipara"
Word_table_cleaned[Word_table_cleaned$Species == "Striped plateau lizard (Sceloporus virgatus)",
                   "Species"] <- "Sceloporus_virgatus"

# Clean up.
rm(list = c("check_species", "check_study", "i", "non_subheader_rows",
            "dupl_row94", "dupl_row112", "dupl_row113", "Word_doc", "Word_table"))

# Create the data object with the name and format expected by the original
# code.
data <- as.data.frame(Word_table_cleaned)
names(data)[names(data) == "Study"] <- "study"
names(data)[names(data) == "Trait"] <- "trait"
names(data)[names(data) == "Species"] <- "species"
names(data)[names(data) == "Zr"] <- "zr"

# Because original data import call would have automatically converted all
# strings to factors, convert all string columns to factors.
data$species <- as.factor(data$species)
data$trait <- as.factor(data$trait)
data$Sex <- as.factor(data$Sex)
data$Stress.measure <- as.factor(data$Stress.measure)
data$Covariates <- as.factor(data$Covariates)
data$study <- as.factor(data$study)

```

# (Re-)run the analysis to reproduce result
```{r analysis}

# Perform required data formatting.
sourceLines(orig_source, 20, 22)

# Import manually created tree file.
tree <- read.tree(file = here::here("original", "MA145_recreated_all_species_cladogram.txt"))

# Check tree file (summarise and plot the tree).
sourceLines(orig_source, 26, 27)

# Set priors.
sourceLines(orig_source, 37, 39)

# Set a random seed to ensure reproducibility of results.
set.seed(145)

# Run the three-random-effects model.
# (Use custom code only to set the option verbose=FALSE to make output
# shorter.)
meta2 <- MCMCglmm(zr~1, random= ~study + species + animal, mev=data$var, data=data,
nitt=3000000, thin=2000, burnin=2000000, pr=TRUE, prior=prior3, pedigree=tree, verbose = FALSE)
#sourceLines(orig_source, 48, 49)

# Get a summary of the model.
# Custom code because the original code only prints this to screen, and doesn't
# capture the model summary object.
meta2_sum <- summary(meta2)
print(meta2_sum)

repro_result_df <- data.frame(ID = "MA145",
                             source = "repro",
                             result_type = "mean",
                             es_type = "Fisher z-transformation of correlation",
                             point_est = round(meta2_sum$solutions[1], 2),
                             hpdi_lower = round(meta2_sum$solutions[2], 2),
                             hpdi_upper = round(meta2_sum$solutions[3], 2),
                             n = meta2$Random$nrl[4],
                             n_studies = meta2$Random$nrl[1],
                             n_species = meta2$Random$nrl[2])
rownames(repro_result_df) <- NULL

knitr::kable(x = repro_result_df)

```

# Compare original and reproduced result
```{r compare}

result_compare <- compare_vars(df_orig = orig_result_df,
                                df_repro = repro_result_df,
                                checkvars = c("point_est",
                                              "hpdi_lower", "hpdi_upper",
                                              "n",
                                              "n_studies", "n_species"))

knitr::kable(x = orig_result_df[, c("ID", "result_type", "es_type")],
             caption = "Details of result")

knitr::kable(x = result_compare,
             caption = "Comparison of original and reproduced values")

# Write results comparison to file.
out1 <- orig_result_df[1, c("ID", "result_type", "es_type")]
out2 <- cbind(out1, result_compare, row.names = NULL)
write.csv(x = out2, file = here::here("output", "MA145_result_comparison.csv"),
          row.names = FALSE)

```

# R session information

```{r rsession}
devtools::session_info()
```
