---
title: "Reproducibility Report for MA065"
author: "Steven Kambouris"
date: "18/09/2021"
output: html_document
knit: (function(input, ...){
    rmarkdown::render(input, output_dir = here::here("output"), envir = globalenv())
  })
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      include = TRUE)
```

# Reproducing result from

Noble, D. W. A., Stenhouse, V., & Schwanz, L. E. (2018). Developmental temperatures and phenotypic plasticity in reptiles: A systematic review and meta‐analysis. _Biological Reviews_, _93_(1), 72–97. https://doi.org/10.1111/brv.12333

# Result to be reproduced

> As predicted, there was a significant negative weighted mean effect size of incubation temperature on incubation duration (_g_ = −8.42, 95% CI = −10.73 to −6.63, _N_ = 703). (Noble et al., 2018, p.80)

```{r orig-result}
orig_result_df <- data.frame(ID = "MA065",
                             source = "original",
                             result_type = "mean",
                             es_type = "Hedges' g",
                             point_est = -8.42,
                             ci_lower = -10.73,
                             ci_upper = -6.63,
                             n = 703)

knitr::kable(x = orig_result_df)
```

# Details of shared data and code files

The following data and code files were shared on OSF:

Noble, D. W., & Schwanz, L. (2018, June 13). _Developmental temperatures and phenotypic plasticity in reptiles: A systematic review and meta-analysis._ https://doi.org/10.17605/OSF.IO/ZBGSS

Noble, D. W. (2018, July 23). _Data._ Retrieved from osf.io/yd8gs 

Noble, D. W. (2017, April 18). _Code._ Retrieved from osf.io/fgkv9 

Noble, D. W. (2018, May 10). _Additional Files._ Retrieved from osf.io/mvvhs 

* inc.csv
* tincdat_fin.csv
* tincNoInc.csv
* analysis_TincMeta.R
* explore_analysis.R
* figures_final.R
* func.R
* phylo_matrices
* SensitivityAnalysis_Matrices.Rdata
* Sinv_matrices
* tree_fin.txt

There is no licencing information available for these files.

# Applicability of shared data and code files

## Data
There were two separate OSF modules containing "data" files: the _Data_ module and the _Additional Files_ module. For the purposes of reproducing the selected result regarding incubation duration, the data file `inc.csv` in the _Data_ module was determined to be the file to use (based on comments in the code file `analysis_TincMeta.R`): the file was referred to directly by name. Additional comments in the same code file indicated that the phylogenetic tree data file `tree_fin.txt` from the _Additional Files_ module was required as well (again, the code referred to the specific file name).

The files `phylo_matrices`, `SensitivityAnalysis_Matrices.Rdata`, and `Sinv_matrices` contain R objects which can be imported to immediately provide the intermediate-stage R objects (phylogenetic correlation and sampling error matrices) required for running the meta-analysis models, and thus save some computation time. However, since it appears that these intermediate-stage objects are not strictly required (the code file `analysis_TincMeta.R` can calculate them from scratch), these R objects will not be used in this result reproduction attempt.

## Code
All four R script files are very clearly structured and have extensive commenting throughout. It was clear from inspection that the code file `analysis_TincMeta.R` (titled "Clean Analysis Code") was the file containing the code to run the meta-analysis models. This file sourced code from the auxiliary code file `func.R` (titled "Functions used throughout analyses and processing of script").

**Note: This version of the reproducibility report does _not_ use the pre-generated data objects (the phylogenetic correlation and sampling error matrices).**

# Set up
```{r library}

# Load packages required for working with original files.
library(here)

# Load custom package for (i) running the source command for specific line
# numbers within a file and (ii) for calculating the percentage error between
# the original and reproduced values.
library(reprohelper)

# Load packages required for data import/cleaning.
# (None required.)

# Load packages required by the code to run.
# (These packages are loaded in the same order as loaded in the original code
# file.)
library(MCMCglmm)
library(plyr)
library(car)
library(ape)

# Set the path to the original code file(s).
orig_source <- here::here("original", "analysis_TincMeta.R")
```

# Import and clean data
```{r importdata}

# Full data set - includes incubation duration
#tincdat_fin <- read.csv(here::here("original", "tincdat_fin.csv"))

# Trait data set - excludes incubation duration
#tincNoInc <- read.csv(here::here("original", "tincNoInc.csv"))

# Incubation duration dataset
inc <- read.csv(here::here("original", "inc.csv"))

# Import the phylogeny and create phylogenetic correlation matrix
phylo <- read.tree(file = here::here("original", "tree_fin.txt"))

```

# (Re-)run the analysis to reproduce result
```{r analysis}

# Load func.R file
# (Custom code due to path differences)
source(here::here("original", "func.R"))

# Phylogenetic correlation matrices

# Format the imported tree
sourceLines(orig_source, 44, 47)

# Prune the tree for the incubation-only dataset
sourceLines(orig_source, 54, 56)

# Create correlation matrices
#sourceLines(orig_source, 59, 59)
sourceLines(orig_source, 61, 61)

# Check trees are ultrametric
#sourceLines(orig_source, 64, 64)
sourceLines(orig_source, 66, 66)

# Calculate inverse of matrices
#sourceLines(orig_source, 69, 69)
sourceLines(orig_source, 71, 71)

# Sampling error matrices

# Full dataset
#sourceLines(orig_source, 78, 79)

# Incubation-only dataset
sourceLines(orig_source, 86, 87)

# Meta-analytic models

# Set MCMC parameters and priors.
sourceLines(orig_source, 106, 112)

# Run model for incubation duration.
set.seed(65)
sourceLines(orig_source, 121, 123)

# Extract summary stats from model (pooled estimate, HPD bounds).
sourceLines(orig_source, 186, 189)

# (Get sample size, it is just the number of rows in the dataset passed to the
# model on line 123.)

repro_result_df <- data.frame(ID = "MA065",
                             source = "repro",
                             result_type = "mean",
                             es_type = "Hedges' g",
                             point_est = round(inc_esPool, 2),
                             ci_lower = round(inc_esPoolL, 2),
                             ci_upper = round(inc_esPoolU, 2),
                             n = nrow(inc))
rownames(repro_result_df) <- NULL

knitr::kable(x = repro_result_df)

```

# Compare original and reproduced result
```{r compare}

result_compare <- compare_vars(df_orig = orig_result_df,
                                df_repro = repro_result_df,
                                checkvars = c("point_est",
                                              "ci_lower", "ci_upper",
                                              "n"))

knitr::kable(x = orig_result_df[, c("ID", "result_type", "es_type")],
             caption = "Details of result")

knitr::kable(x = result_compare,
             caption = "Comparison of original and reproduced values")

# Write results comparison to file.
out1 <- orig_result_df[1, c("ID", "result_type", "es_type")]
out2 <- cbind(out1, result_compare, row.names = NULL)
write.csv(x = out2, file = here::here("output", "MA065_result_comparison.csv"),
          row.names = FALSE)

```

# R session information

```{r rsession}
devtools::session_info()
```
