---
title: "Reproducibility Report for MA213"
author: "Steven Kambouris"
date: "18/09/2021"
output: html_document
knit: (function(input, ...){
    rmarkdown::render(input, output_dir = here::here("output"), envir = globalenv())
  })
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE,
                      include = TRUE)
```

# Reproducing result from

Colautti, R. I., & Lau, J. A. (2015). Contemporary evolution during invasion: Evidence for differentiation, natural selection, and local adaptation. _Molecular Ecology_, _24_(9), 1999–2017. https://doi.org/10.1111/mec.13162

# Result to be reproduced

> The average difference between the introduced and native range (i.e. effect size) of our hypothetical trait was small (-0.07) and nonsignificant (P = 0.362) when all sample sites were pooled in our analysis (N = 654). (Colautti & Lau, 2015, p.2004)

```{r orig-result}
orig_result_df <- data.frame(ID = "MA213",
                             source = "original",
                             result_type = "mean",
                             es_type = "difference in means",
                             point_est = -0.07,
                             p_value = 0.362,
                             n = 654)

knitr::kable(x = orig_result_df)
```

# Details of shared data and code files

The following data and code files were shared on Dryad:

Colautti, R. I., & Lau, J. A. (2015). _Data from: Contemporary evolution during invasion: Evidence for differentiation, natural selection, and local adaptation._ Dryad Digital Repository. https://doi.org/10.5061/dryad.gt678

* ClinesModel.r
* MetaPCA_Analysis.r
* MetaPCA_Data.csv
* README_for_MetaPCA_Data.txt
* README_for_Selection_Data.txt
* README_for_SpatialStructure_Data.txt
* Selection_Analysis.R
* Selection_Data.csv
* SpatialStructure_Analysis.R
* SpatialStructure_Data.csv

These files are licensed under a [CC0 1.0 Universal (CC0 1.0) Public Domain Dedication](https://creativecommons.org/publicdomain/zero/1.0/) license.

# Applicability of shared data and code files

## Data
The usage notes on the Dryad repository web page note that `SpatialStructure_Analysis.R` is the code applicable to the analysis presented in Box 1 of the article (on page 2004), see below. Given that information, the data file named `SpatialStructure_Data.csv` is logically named to be the relevant data file. The file `README_for_SpatialStructure_Data.txt` makes explicit that `SpatialStructure_Data.csv` is analysed by `SpatialStructure_Analysis.R`, and also describes the variables found in the file.

## Code
The usage notes on the Dryad repository web page note that `SpatialStructure_Analysis.R` is the code applicable to the analysis presented in Box 1 of the article (on page 2004). The code file contains enough comments to be able to follow the relevant parts of the analysis to reproduce the selected result.

# Set up
```{r library}

# Load packages required for working with original files.
library(here)

# Load custom package for (i) running the source command for specific line
# numbers within a file and (ii) for calculating the percentage error between
# the original and reproduced values.
library(reprohelper)

# Load packages required for data import/cleaning.
# (None required.)

# Load packages required by the code to run.
# (These packages are loaded in the same order as loaded in the original code
# file.)
library(ggplot2)
library(scales)

# Set the path to the original code file(s).
orig_source <- here::here("original", "SpatialStructure_Analysis.R")
```

# Import and clean data
```{r importdata}

# Import the data from CSV (custom code required to deal with path issues)
Locs <- read.csv(here::here("original", "SpatialStructure_Data.csv"),
                 header=TRUE)

```

# (Re-)run the analysis to reproduce result
```{r analysis}

# Show data.
sourceLines(orig_source, 6, 6)

# Format data.
sourceLines(orig_source, 8, 19)

# Calculate p-values for the full data set.
# The t-test is all that's needed for this result.
sourceLines(orig_source, 21, 23)

# The test performed uses the Welch two-sample t-test. The sample size can't be
# extracted from the test output object, so just take the number of rows from
# the Locs data frame as the number of studies value.

repro_result_df <- data.frame(ID = "MA213",
                             source = "repro",
                             result_type = "mean",
                             es_type = "difference in means",
                             point_est = round(FullTtest$estimate[1] - FullTtest$estimate[2], 2),
                             p_value = round(FullTtest$p.value, 3),
                             n = dim(Locs)[1])
rownames(repro_result_df) <- NULL

knitr::kable(x = repro_result_df)

```

# Compare original and reproduced result
```{r compare}

result_compare <- compare_vars(df_orig = orig_result_df,
                                df_repro = repro_result_df,
                                checkvars = c("point_est",
                                              "p_value",
                                              "n"))

knitr::kable(x = orig_result_df[, c("ID", "result_type", "es_type")],
             caption = "Details of result")

knitr::kable(x = result_compare,
             caption = "Comparison of original and reproduced values")

# Write results comparison to file.
out1 <- orig_result_df[1, c("ID", "result_type", "es_type")]
out2 <- cbind(out1, result_compare, row.names = NULL)
write.csv(x = out2, file = here::here("output", "MA213_result_comparison.csv"),
          row.names = FALSE)

```

# R session information

```{r rsession}
devtools::session_info()
```
